Assessing landscape N removal in coastal New England catchments using the N-Sink

### 2023-04-27 manuscript/manuscript.Rmd
eval true

```{r get-data, eval=FALSE, cache=FALSE, include=FALSE}
# eval = TRUE if you want to download the data
# Get data for selected HUC
niantic_download <- nsink_get_data(niantic_huc_id, 
                                  data_dir = "nsink_niantic_data/")
```

>>>>

```{r get-data, eval=TRUE, cache=FALSE, include=FALSE}
# eval = TRUE if you want to download the data
# Get data for selected HUC
niantic_download <- nsink_get_data(niantic_huc_id, 
                                  data_dir = "nsink_niantic_data/")
```
